A Systematic Review of the Use of the ESM Methodology in Education

### 2020-09-14 paper_draft.Rmd
Table up to date

The literature search for this study was conducted over 2 databases, EBSCO and SCOPUS. We searched for all articles including the terms “ESM”, “Experience Sampling” “Experience Sampling Method”, “Experience Sampling Approach”, “Experience Sampling Study”, and “Experience Sampling Studies”. To find out the articles, use used 2 different search query for the two databases. 
In EBSCO database the search query we used is “"experience sampling" N3 (method* OR approach* OR study OR studies)” and initially found 345 results. Then we go through the title, keywords and abstract for each article carefully and find out if they are on education and have used ESM as their data collection method. After our first screening, we found 128 articles that looked relevant to this study. 
Then we searched in the Scopus database and we used "Experience Sampling Method"  AND  (education  OR  learning  OR  instruction  OR  teach*  OR  student* ) as our search in this database. We initially found 197 results from this search. After screening them to find out whether they are on education and have used ESM as their data collection method, we found 77 relevant articles, that looks in scope for this study. 
Therefore, we have 205 articles from two search. However, there are some duplicates articles as we pulled the articles from two different database. After deleting the duplicates, we primarily found 162 articles for this study. We also include 8 articles from an individual search that was done prior to EBSCO and Scopus database search. As a result, we have 180 articles in total to code for this study. However, when started coding them, we found some articles are not in our scope. For example, Ito (2016) paper’s target group is students and they used ESM, but they explore students’ leisure experience using ESM. That’s why we did not include this article in our study. Moreover, some of the articles have used same datasetes. In those cases, we have coded the articles that was published first (example???). Finally, after coding the articles, we have XXX articles that are in our study scope.

@@

|Element          |Steps Taken                                            |
|-----------------|-------------------------------------------------------|
|Sampling strategy|Comprehensive search for all journal articles about ESM|
|Type of study    |Search of the EBSCO database and SCOPUS database       |
|Approaches	      |Search of the EBSCO database and SCOPUS database       |
|Range of years   |1989 to 2020                                           |
|Limits           |Published in the english language                      |

>>>>

The literature search for this study was conducted over 2 databases, EBSCO and SCOPUS. We searched for all articles including the terms “ESM”, “Experience Sampling” “Experience Sampling Method”, “Experience Sampling Approach”, “Experience Sampling Study”, and “Experience Sampling Studies”. To find out the articles, use used 2 different search query for the two databases. 
In EBSCO database the search query we used is “"experience sampling" N3 (method* OR approach* OR study OR studies)” and initially found 345 results. Then we go through the title, keywords and abstract for each article carefully and find out if they are on education and have used ESM as their data collection method. After our first screening, we found 128 articles that looked relevant to this study. 
Then we searched in the Scopus database and we used "Experience Sampling Method"  AND  (education  OR  learning  OR  instruction  OR  teach*  OR  student* ) as our search in this database. We initially found 197 results from this search. After screening them to find out whether they are on education and have used ESM as their data collection method, we found 77 relevant articles, that looks in scope for this study. 
Therefore, we have 205 articles from two search. However, there are some duplicates articles as we pulled the articles from two different database. After deleting the duplicates, we primarily found 162 articles for this study. We also include 8 articles from an individual search that was done prior to EBSCO and Scopus database search. As a result, we have 180 articles in total to code for this study. However, when started coding them, we found some articles are not in our scope. For example, Ito (2016) paper’s target group is students and they used ESM, but they explore students’ leisure experience using ESM. That’s why we did not include this article in our study. Moreover, some of the articles have used same data-set. In those cases, we have coded the articles that was published first (example???). Finally, after coding the articles, we have XXX articles that are in our study scope.

@@

|Element           |Steps Taken                                            |
|------------------|-------------------------------------------------------|
|Sampling strategy |Comprehensive search for all journal articles about ESM|
|Type of study     |Search of the EBSCO database and SCOPUS database       |
|Approaches	       |Search of the EBSCO database and SCOPUS database       |
|Range of years    |1989 to 2020                                           |
|Limits            |Published in the english language                      |
|Inclusion criteria|“ESM”, “Experience Sampling” “Experience Sampling Method”, “Experience Sampling Approach”, “Experience Sampling Study”, or “Experience Sampling Studies” are included in the title, keyword or abstract           |
|Terms used        |“ESM”, “Experience Sampling” “Experience Sampling Method”, “Experience Sampling Approach”, “Experience Sampling Study”, and “Experience Sampling Studies”                                                          |
|Electronic sources|The citation reference software Endnote                |
